Imaging of cortical oxygen tension and blood flow following targeted photothrombotic stroke

### 2018-06-23 article.tex
Added highlights to new changes

\subsection{Limitations}
A potential concern for this system is the scattering of light beyond the desired region of interest when performing the \pO\ measurements or targeted photothrombosis. This problem is highlighted by the discrepancies seen in \pO\ values under 445 nm and 637 nm illumination and introduces the risk of collateral tissue damage. The wavelength dependence of light propagation also means the LSCI and \pO\ measurements sample different volumes of tissue. The use of anesthesia during imaging significantly affects systemic hemodynamics \cite{Janssen:2004ih} and has been shown to inhibit the oxygen autoregulatory response \cite{Aksenov:2012wh}. The implementation of an awake imaging setup \cite{Dombeck:2007gr} would resolve this issue by completely eliminating the need for anesthesia during imaging. Another concern is that estimates of blood flow provided by single-exposure speckle imaging have limitations for chronic imaging or cross-animal comparisons \cite{Kazmi:2013hp}. An enhanced technique known as Multi-Exposure Speckle Imaging (MESI) has been developed to increase the quantitative accuracy of flow measurements \cite{Parthasarathy:2008el}. Implementing MESI would allow for more robust chronic measurements of blood flow in the ischemic brain.

>>>>

\subsection{Limitations}
A potential concern for this system is the scattering of light beyond the desired region of interest when performing the \pO\ measurements or targeted photothrombosis. This problem is highlighted by the discrepancies seen in \pO\ values under 445 nm and 637 nm illumination and introduces the risk of collateral tissue damage. The wavelength dependence of light propagation also means the LSCI and \pO\ measurements sample different volumes of tissue. The use of anesthesia during imaging significantly affects systemic hemodynamics \cite{Janssen:2004ih} and has been shown to inhibit the oxygen autoregulatory response \cite{Aksenov:2012wh}. \textcolor{red}{Because the animals are used for chronic imaging, tracheal intubation for mechanical ventilation is not an option. This may introduce inconsistencies in breathing that can skew both blood flow and \pO\ measurements.} The implementation of an awake imaging setup \cite{Dombeck:2007gr} would resolve these issue by completely eliminating the need for anesthesia during imaging. Another concern is that estimates of blood flow provided by single-exposure speckle imaging have limitations for chronic imaging or cross-animal comparisons \cite{Kazmi:2013hp}. An enhanced technique known as Multi-Exposure Speckle Imaging (MESI) has been developed to increase the quantitative accuracy of flow measurements \cite{Parthasarathy:2008el}. Implementing MESI would allow for more robust chronic measurements of blood flow in the ischemic brain.
